DeepSphere: a graph-based spherical CNN

### 2019-11-13 main.tex
update checklist

\todo{
\begin{itemize}
% 	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN. [Yes]
% 	\item adjacency matrix: $A$ instead of $W$? nath: I am for W
% 	\item anonymize DeepSphere citation - Not doing that
% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
	\item citet for inline, citep for parenthesis
	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method.
	\item PSD of climate data: how does it compare to cosmo and 3D objects?
	\item align the spheres in figure 1
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
	\item check footnotes
	\item climate data on spectrum plot
	\item result tables: only what supports the main message in the text, everything we have in the appendix
	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
	\item check English vs American English
	\item unify enumerations. I like (i), (ii), etc.
	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness?
	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere.
	\item figure placements
	\item do the experiments on the icosahedral grid with the pooling as defined in the paper
	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
	\item update pygsp and merge sphere branch
	\item check that NN architectures and hyper-params are correctly reported
	\item keep NN architecture and hyper-params in the main text? Move the paragraph to appendix if not enough space.
	%\item shall we still site adam and batch norm? no, mainstream enough
	\item check results for ModelNet40 and integrate in text
	\item Check that HEALPix is introduced in the introduction
	\item heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison.
% 	\item check experiments section [Frédérick]: all the results numbers and NN + training details
	\item compute the invariance error of the whole NNs (before and after training, invariance can be learned)
	\item add it with equivariance error of the convolution to \tabref{cosmo}
	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
\end{itemize}
}

>>>>

\todo{
\begin{itemize}
% 	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN. [Yes]
% 	\item adjacency matrix: $A$ instead of $W$? nath: I am for W
% 	\item anonymize DeepSphere citation - Not doing that
% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
	\item citet for inline, citep for parenthesis
	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method. \nati{I would drop this.}
	\item PSD of climate data: how does it compare to cosmo and 3D objects?
	\item align the spheres in figure 1
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
	\item check footnotes
	\item climate data on spectrum plot \nati{I would drop this}
	\item result tables: only what supports the main message in the text, everything we have in the appendix \nati{I think this is done now}
	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
	\item check English vs American English
	\item unify enumerations. I like (i), (ii), etc.
	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness? \nati{I think this is already done.}
	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere. \nati{Where do you want to add them?}
	\item figure placements \nati{Good according to me}
	\item do the experiments on the icosahedral grid with the pooling as defined in the paper \nati{I guess we are not doing that.}
	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
	\item update pygsp and merge sphere branch
	\item check that NN architectures and hyper-params are correctly reported
	\item keep NN architecture and hyper-params in the main text? Move the paragraph to appendix if not enough space. \nati{I think this does not apply anymore}
	%\item shall we still site adam and batch norm? no, mainstream enough
	\item check results for ModelNet40 and integrate in text \nati{I would drop this}
	\item Check that HEALPix is introduced in the introduction
	\item heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison.  \nati{Bit syre what you mean here...}
% 	\item check experiments section [Frédérick]: all the results numbers and NN + training details
	\item compute the invariance error of the whole NNs (before and after training, invariance can be learned) \nati{I guess we are not doing that}
	\item add it with equivariance error of the convolution to \tabref{cosmo}
	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
\end{itemize}
}
